Dynamical modeling of tidal streams

### 2013-12-26 tex/ms.tex
streams: more captions and tweaks to aa description

The left panel of \figurename~\ref{fig:aAI} shows a running average of
the radial action calculated using \eqnname~(\ref{eq:aAIJ}) along the
orbit of the progenitor in the simulation used in the main body of
this paper. The time in this figure is in units of $35.56\Myr$, so the
orbit is integrated for a total of $7.11\Gyr$. After a few radial
periods, the radial action quickly converges with a remaining
oscillatory behavior that is primarily a function of the radial angle,
but that becomes smaller over time. With longer integrations and
shorter time-steps, the radial action can converge to any desired
tolerance. The duration of the orbit integration shown in this figure
is what is typically used in this paper and gives a precision of
$\approx2\,\%$ in the actions.

@@

\begin{figure}[t!]
 \includegraphics[width=0.48\textwidth,clip=]{aAI_jr.ps}
 \includegraphics[width=0.48\textwidth,clip=]{aAI_araz.ps}
  \caption{}\label{fig:aAI}
%python plot_aAI.py ../tex/aAI_jr.ps
%python plot_aAI.py ../tex/aAI_araz.ps
\end{figure}

>>>>

The left panel of \figurename~\ref{fig:aAI} shows a running average of
the radial action calculated using \eqnname~(\ref{eq:aAIJ}) along the
orbit of the progenitor in the simulation used in the main body of
this paper. The time in this figure is in units of $35.56\Myr$, so the
orbit is integrated for a total of $7.11\Gyr$. The auxiliary isochrone
potential has a scale parameter of $6.4\kpc$. After a few radial
periods, the radial action quickly converges with a remaining
oscillatory behavior that is primarily a function of the radial angle,
but that becomes smaller over time. With longer integrations and
shorter time-steps, the radial action can converge to any desired
tolerance. The duration of the orbit integration shown in this figure
is what is typically used in this paper and gives a precision of
$\approx2\,\%$ in the actions.

@@

\begin{figure}[t!]
 \includegraphics[width=0.48\textwidth,clip=]{aAI_jr.ps}
 \includegraphics[width=0.48\textwidth,clip=]{aAI_araz.ps}
  \caption{Action--angle calculations using an orbit-integration-based
    method. The right panel shows the cumulative mean of the radial
    actions calculated in an auxiliary isochrone potential calculated
    along the orbit of the progenitor used in the main body of this
    paper. The color-coding corresponds to the radial angle
    (calculated in the isochrone potential) along the orbit. The time
    is in units of $35.56\Myr$ and the radial action is normalized by
    its value at $t=200$. The left panel shows the radial and vertical
    angles calculated in the auxiliary isochrone potential, with
    color-coding corresponding to the azimuthal angle. The wiggles in
    the angles are due to the isochrone potential not being the
    correct potential, but these wiggles are fit and removed to
    calculate the true angles.}\label{fig:aAI}
%python plot_aAI.py ../tex/aAI_jr.ps
%python plot_aAI.py ../tex/aAI_araz.ps
\end{figure}
